\vspace{-1cm}\normalsize{\textbf{Fairly Random: Impact of Winning the Toss on the Probability of Winning}}

### 2015-09-19 write_up/cricket.tex
added cite to dw etc.

\section*{Data}
Data are from 43,185 first-class men's cricket matches.\footnote{You can find the scripts used to scrape the data, the final data set, and scripts used for analysis at: \href{http://github.com/soodoku/get-cricket-data/}{http://github.com/soodoku/get-cricket-data/}.} It is a near census of the relevant population. We have data on all types of matches: domestic and international Twenty20s -- T20 and T20I respectively, domestic and international one-dayers -- List A and One-Day Internationals (ODI) respectively, and domestic and international multi-day matches -- First Class (FC) and Tests respectively.\footnote{There is a rich variety of first-class matches. In English county cricket, first-class matches last four days. Some first class matches last just a day. Others two days. Yet others three days. And till a particular point in history, a test match lasted as long as it was needed to finish a game. We elide over such differences.}

@@

In limited over matches sometimes weather intervenes significantly after the match has already begun. After certain loss of time, the match is generally curtailed and the scores adjusted using a method invented by Duckworth and Lewis. We can use the random nature of who wins the toss to see if winning percentages are strongly conditioned by matches that use Duckworth Lewis and matches that don't. We find scant differences except in the case of international Twenty20s (see Figure ~\ref{fig:dl}).

\begin{figure}[htbp]
\centering
\caption{Percentage of Matches Won Minus Matches Lost After Winning the Toss by Duckworth Lewis}
\includegraphics[scale=.85]{../figs/winbyDL.pdf}
\label{fig:dl}
\end{figure}

>>>>

\section*{Data}
Data are from 43,185 first-class men's cricket matches.\footnote{You can find the scripts used to scrape the data, the final data set, and scripts used for analysis at: \href{https://github.com/dwillis/cricket-stats}{https://github.com/dwillis/cricket-stats}.} It is a near census of the relevant population. We have data on all types of matches: domestic and international Twenty20s -- T20s and T20Is respectively, domestic and international one-dayers -- List A and One-Day Internationals (ODI) respectively, and domestic and international multi-day matches -- First Class (FC) and Tests respectively.\footnote{There is a rich variety of first-class matches. In English county cricket, first-class matches last four days. Some first class matches last just a day. Others two days. Yet others three days. And till a particular point in history, a test match lasted as long as it was needed to finish a game. We elide over such differences.}

@@

In limited over matches sometimes weather intervenes significantly after the match has already begun. After certain loss of time, the match is generally curtailed and the scores adjusted using a method invented by Duckworth and Lewis \citep[see][]{duckworth1998}. We can use the random nature of who wins the toss to see if winning percentages are strongly conditioned by matches that use Duckworth-Lewis and matches that don't. We find scant differences except in the case of international Twenty20s (see Figure ~\ref{fig:dl}).

\begin{figure}[htbp]
\centering
\caption{Percentage of Matches Won Minus Matches Lost After Winning the Toss by Duckworth-Lewis}
\includegraphics[scale=.85]{../figs/winbyDL.pdf}
\label{fig:dl}
\end{figure}
